MS_CNuptake.Rmd

### 2023-03-30 MS_CNuptake.Rmd
small updaet

# for all logit function model (mod_tnpp, mod_anpp, mod_lnpp, nre_model): a = 1/(1+exp(-b)), where a is the ratio (e.g. npp/gpp) and b is the regression (e.g. mod =tnpp)
#we calculate uncertainty of b firstly, based on each regression
#now we need to calculate deriative a / deriative b, based on a = 1/(1+exp(-b)). After calculation it is: exp(-b) / ( (1 + exp(-b)) ^2)

>>>>

# for all logit function model (mod_tnpp, mod_anpp, mod_lnpp, nre_model): a = 1/(1+exp(-b)), where a is the ratio and b is the regression 
#we calculate uncertainty of b firstly, based on each regression
#now we need to calculate deriative a / deriative b, based on a = 1/(1+exp(-b)). After calculation it is: exp(-b) / ( (1 + exp(-b)) ^2)
